### 2018-04-20 paper/paper.tex
Resolve the conflict

\paragraph
2The following plots demonstrate the results of Logistic Regression with degree 1 and learning rate $\eta$ = 1 for 20 and 2000 iterations :

\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter20.png}
	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter20_error.png}
	\caption{iteration = 20}
\end{figure}
\clearpage
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter2000.png}
	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter2000_error.png}
	\caption{iteration = 2000}
\end{figure}

@@

When the number of iterations is too low, the logistic regression process finishes before reaching the local minima.When the number of iterations is too high, it takes a lot of time. Even though it reaches the local minima, it continues to iterate until it reaches the iteration number. Therefore, the number of iterations should not be too low and high.
\paragraph
3 The following plots demonstrate the results of Logistic Regression with degree = 2 , iterations = 200 and learning rate $\eta$ = \{.15, 1.5, 15.\} :
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta015.png}
	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta015_error.png}
	\caption{learing rate $\eta$ = .15}
\end{figure}
\clearpage
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta105.png}
	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta105_error.png}
	\caption{learing rate $\eta$ = 1.5}
\end{figure}
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta15.png}
	\includegraphics[width=0.5\textwidth]{logreg_deg2_iter200_eta15_error.png}
	\caption{learing rate $\eta$ = 15}
\end{figure}

@@

\paragraph
4 These are  good pairs of values for the number of iterations and learning rate for each degree in l ∈{1,2,5,15} that provides a good solution in reasonable time\\
\textbf{Degree $l$ = 1 :}\\
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{best_fit_degree1.png}
	\includegraphics[width=0.5\textwidth]{best_fit_degree1_error.png}
	\caption{learing rate $\eta$ = 1, iteration = 100}
\end{figure}\\
\textbf{Degree $l$ = 2 :}\\
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{best_fit_degree2.png}
	\includegraphics[width=0.5\textwidth]{best_fit_degree2_error.png}
	\caption{learing rate $\eta$ = 0.5, iteration = 700}
\end{figure}
\textbf{Degree $l$ = 5 :}\\
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{best_fit_degree5.png}
	\includegraphics[width=0.5\textwidth]{best_fit_degree5_error.png}
	\caption{learing rate $\eta$ = 0.5, iteration = 2000}
\end{figure}
\textbf{Degree $l$ = 5 :}\\
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{best_fit_degree15.png}
	\includegraphics[width=0.5\textwidth]{best_fit_degree15_error.png}
	\caption{learing rate $\eta$ = 0.5, iteration = 2000}
\end{figure}

>>>>

\paragraph
2 The following plots demonstrate the results of Logistic Regression with degree 1 and learning rate $\eta$ = 1 for 20 and 2000 iterations :

\paragraph
\\
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter20.png}
	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter20_error.png}
	\caption{iteration = 20}
\end{figure}
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter2000.png}
	\includegraphics[width=0.5\textwidth]{logreg_deg1_iter2000_error.png}
	\caption{iteration = 2000}
\end{figure}

@@

When the number of iterations is too low, the logistic regression process finishes before reaching the local minima.When the number of iterations is too high, it takes a lot of time. Even though it reaches the local minima, it continues to iterate until it reaches the iteration number. Therefore, the number of iterations should not be too low and high.
\paragraph
3 The following plots demonstrate the results of Logistic Regression with degree = 2 , iterations = 200 and learning rate $\eta$ = \{.15, 1.5, 15.\} :
\clearpage
\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta015.png}
	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta015_error.png}
	\caption{learing rate $\eta$ = .15}
\end{figure}
\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta105.png}
	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta105_error.png}
	\caption{learing rate $\eta$ = 1.5}
\end{figure}
\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta15.png}
	\includegraphics[width=0.4\textwidth]{logreg_deg2_iter200_eta15_error.png}
	\caption{learing rate $\eta$ = 15}
\end{figure}

@@

\paragraph
4 These are  good pairs of values for the number of iterations and learning rate for each degree in l ∈{1,2,5,15} that provides a good solution in reasonable time\\
\clearpage
\textbf{Degree $l$ = 1 :}\\
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{best_fit_degree1.png}
	\includegraphics[width=0.5\textwidth]{best_fit_degree1_error.png}
	\caption{learing rate $\eta$ = 1, iteration = 100}
\end{figure}\\
\textbf{Degree $l$ = 2 :}
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{best_fit_degree2.png}
	\includegraphics[width=0.5\textwidth]{best_fit_degree2_error.png}
	\caption{learing rate $\eta$ = 0.5, iteration = 700}
\end{figure}
\clearpage
\textbf{Degree $l$ = 5 :}
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{best_fit_degree5.png}
	\includegraphics[width=0.5\textwidth]{best_fit_degree5_error.png}
	\caption{learing rate $\eta$ = 0.5, iteration = 2000}
\end{figure}\\
\textbf{Degree $l$ = 15 :}\\
\begin{figure}[h]
	\includegraphics[width=0.5\textwidth]{best_fit_degree15.png}
	\includegraphics[width=0.5\textwidth]{best_fit_degree15_error.png}
	\caption{learing rate $\eta$ = 0.5, iteration = 2000}
\end{figure}
